 \cventry
    {Public Health Scotland} % Organization
    {Information Analyst} % Job title
    {UK, Edinburgh} % Location
    {Nov 2019 - Mar 2021} % Date(s)
    {
        \textbf{Accident and Emergency}\newline
        I produced weekly, monthly and annual publications for the A\&E team 
        which are presented to a range of different people from the Scottish 
        Government to the general public and media. I had responsibilities in 
        producing new reports and answering information requests. This involves 
        having to balance delivering against a number of on-going, often 
        requested in quick succession and with different level of urgency. I 
        had to understand the importance of each and prioritise work and 
        negotiate deadlines. I also to developed on the work of others and 
        update previous requests to fit new demands.\newline
        \textbf{Drug and Alcohol Treatment Waiting Times}\newline
        I produce monthly management reports as well as quarterly and annual 
        publications where I had to understand the publication process carried 
        out within PHS. I also worked on developing the new Drug and Alcohol 
        System DAISy. Here I had been part of focus groups determining what 
        functionality is best needed for the system from both a data collection 
        and an analytical point of view. I developed the Open Data publication 
        for the DATWT team.\newline
        \textbf{System Watch}\newline
        I work with other analysts to produce daily data that provides boards 
        and management with very up to date data and insights into the 
        pressures in the health care system. Some of this data is shared 
        amongst other PHS teams including HPS COVID teams. I am currently 
        working on developing this system through testing to improve the 
        robustness of the system with time.\newline
}
