 \cventry
{Public Health Scotland} % Organization
{Healthcare Scientist (Epidemiologist)} % Job title
{UK, Scotland} % Location
{Mar 2021 - Present} % Date(s)
{
In this role, I help PHS to better understand COVID-19 vaccine failure events as well as analysing vaccine effectiveness.\newline
One of my main tasks is to produce and maintain regularly published work. This includes output for the general public, health board chief executives, and other management reports. This involves collaborating closely with the data manager in the team to extract data from a range of datasets, join and mutate the data into a form that can be used for publication. With this formatted, I then analyse the data and produce visualisations that best fit the public health messages arising from the analysis. These outputs are then usually formatted into an Rmarkdown document which can be used by all members of our team to produce up to data analyses. With these reports I provide analytical and scientific interpretation to the data, helping the consumer to better understand what is being presented.\newline
Recently I have been the lead in moving and advancing our public-facing publication process by producing an interactive R shiny dashboard to display data, analysis, and scientific interpretation. This will not only improve the end product received by the public as they will have more freedom to interact with the data but will also help the team as a whole in answering freedom of information requests as raw data will be more readily available.\newline
I also give regular produce and occasionally present presentations to health board chief executives and senior clinicians along with others to help inform them as to the latest outbreak, case, hospitalisation, and death information related to COVID-19. This involves pulling together information from various sources to provide a relevant description of how the vaccine is affecting COVID-19 related events within care homes. I also provide detailed and evidenced input to the discussion following presentations as to what actions should be taken.\newline
I have also contributed and co-authored peer-reviewed publication produced within our team collaboration with academic colleagues. This publication characterising COVID-19 related deaths in Scotland.\newline
While working in this role I have also provided training to other colleagues within Public Health Scotland. I help to deliver the 'Introduction to git' training course. For this, I work with a team of trainers to help develop the overall course that is being delivered, then with one other deliver the course to a group of ~8 participants where we cover the basics of git and that form of version control. Following the course, we hold questions and feedback sessions where we help to answer people's questions.\newline
}
