
\cvsection{Employment}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------


\begin{cventries}
 \cventry
{Public Health Scotland} % Organization
{Healthcare Scientist (Epidemiologist)} % Job title
{UK, Scotland} % Location
{Mar 2021 - Present} % Date(s)
{
  As a healthcare scientist I have worked on Scotland's COVID-19 response by providing real time data and analysics, guidance, and public facing information on vaccine effectiveness and failures.\newline
  I have worked to develop surveillance systems that collect data from a range of data streams and combined them in novel ways to produce meaning from the data. I then clean, prepare, and analyse the data to be presented using a range of formats. These include written reports (one example can be found here: \href{https://publichealthscotland.scot/publications/covid-19-statistical-report/}{\textit{PHS COVID-19 weekly statistical report}}), presentations to partners, consultants and chief executives, and interactive web based dashboards.
}

\cventry
{Public Health Scotland}
{Information Analyst}
{UK, Scotland}
{Nov 2019 - Mar 2021}
{
            \textbf{Accident and Emergency}\newline
        I produced weekly, monthly and annual publications for the A\&E team, which are presented to a range of different people from the Scottish Government to the general public and media. I had responsibilities in producing new reports and answering information requests. This involves having to balance delivering against a number of on-going projects, often requested in quick succession. I had to understand the importance of each and prioritise work and negotiate deadlines.\newline
        \textbf{Drug and Alcohol Treatment Waiting Times}\newline
        I produced monthly management reports as well as quarterly and annual publications where I had to understand the publication process carried out within PHS. I also worked on developing the new Drug and Alcohol Information System DAISy. Here I had been part of focus groups determining what functionality is best needed for the system from both a data collection and an analytical point of view. I developed the Open Data publication for the Drug and Alcohol Treatment Waiting Times team.\newline
        \textbf{System Watch}\newline
        I work with other analysts to produce daily data that provides boards and management with very up to date data and insights into the pressures in the health care system. Some of this data is shared amongst other PHS teams including HPS COVID teams. I am currently working on developing this system through testing to improve the robustness of the system with time.\newline
}

  \cventry
    {RYA Scotland} % Organization
    {Laser Performance Team Head Coach} % Job title
    {UK, Scotland} % Location
    % {Jul. 2017 - Present} % Date(s)
    {2017 - Present} % Date(s)
    {
        I organise and deliver coaching sessions to the top youth (u21) sailors in Scotland. This involves communication with governing bodies, host venues and participants to organise each session. Each year I work with the sailors in the team to plan out a training program to allow them to perform at their best in the coming season and future careers. I have to work with them to set goals, plan for contingencies, and evaluate success at all points throughout their journeys.\newline
        Within this role, I have coached four UK national championship medallists, with one of my sailors this year being invited to be part of the UK's Olympic pathway program.\newline
     }
       \cventry
    {RYA Scotland} % Organization
    {Laser Class Academy Head Coach} % Job title
    {UK, Scotland} % Location
    % {Jul. 2018 - PRESENT} % Date(s)
    {2018 - Present} % Date(s)
    {
        In this role, I organise, plan and deliver open training to sailors across Scotland. I have to liaise with host venues as well as communicating with the governing body and participants to organise training sessions. I lead a team of assistant coaches that I work with throughout the year. I have the responsibility for mentoring and helping these coaches develop their own coaching abilities. We hold a regular community of practice sessions with other coaches to share our experiences and develop our own abilities. I have taken a lead role in the set up and organisation of these continued professional development sessions.\newline
        I have also had the responsibility of working with the national governing body to produce COVID secure working guidelines to allow for our safe return to on the water coaching sessions.\newline
    }

\end{cventries}

