%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Laser Development Team Head Coach} % Job title
    {RYA Scotland} % Organization
    {UK, Scotland} % Location
    {Jul. 2017 - PRESENT} % Date(s)
    {
      Responsible for developing Scotland’s top youth (U19) Laser sailors to achieve their potential through leading regular training camps and providing coaching support at major events. This involves identifying key areas where performance can be improved; finding solutions to challenging problems that may not have been seen before, and working with a range of personalities to bring everyone together as a team. Key skills I can demonstrate within this role include problem solving, motivation, team development, teaching, coaching, time, risk and project management. Clear goals with measurable, time bound outcomes are essential when delivering this role. 
    }

%---------------------------------------------------------
  \cventry
    {Laser Class Academy Head Coach} % Job title
    {RYA Scotland} % Organization
    {UK, Scotland} % Location
    {Jul. 2018 - PRESENT} % Date(s)
    {
      Within this position I am responsible for organising and delivering open training programmes that are available to all ages. I organize the coaching team to deliver a common goal irrespective of the sailors’ ability.  This adaptive style of coaching has translated into other areas of my life, when working with a team, as it has helped me to quickly identify people's areas of strength and weakness. This can be used to identify where people will be appropriately challenged so as to get the best from them. 
    }

%---------------------------------------------------------
  \cventry
    {Physics Undergraduate Student} % Job title
    {The University of Edinburgh} % Organization
    {UK, Edinburgh} % Location
    {Sept. 2015 - Exp. May. 2019} % Date(s)
    {
      While studying at the University of Edinburgh I have taken a range of courses which have developed many different skills. 
      \begin{itemize}
          \item Computing and Data Analysis.
          \item Problem Solving.
          \item Independent Learning
          \item Critical Thinking.
      \end{itemize}
      During my degree I have had a wide range of experiences. I have developed my mathematical skills by choosing maths for physics courses including Dynamics and Vector Calculus, Fourier Analysis and Statistics, Algebra and Calculus. This prepared me for courses in Quantum Physics and Electromagnetism. In addition I have been involved with projects which cover more niche areas. I worked as part of a team to develop a quantum computer simulator using Python. I completed projects where $\it{Scikit\space Learn}$  was used to set up a machine learning weather prediction system. In my final year I undertook a project that made a comparison of different methods that could be used to estimate the redshifts of galaxies. This combined many skills in to one project. In depth research was required to gain an understanding of the different methods. Machine learning for some of the methods so a working understanding of the methods that were employed here were needed. Lastly, data analysis skills were used to quantitatively and qualitatively compare and understand the results of the project.
    % Maybe add some kind of concluding sentence about how uni has prepared me for stuff?
    }

%---------------------------------------------------------
  \cventry
    {Associate Instructor (Sailing)} % Job title
    {Sport Scotland, Cumbrae} % Organization
    {UK, Cumbrae (North Ayrshire)} % Location
    {Apr. 2015 - PRESENT} % Date(s)
    {
      As an associate instructor I provide a teaching role for Sport Scotland Cumbrae, where I work as part of a team with other instructors to deliver a range of RYA sailing courses from complete beginner to advanced racing. In this role I often give people their first experiences trying a new activity where they need to learn a new and unfamiliar set of skills.
    }

%---------------------------------------------------------
 \cventry
    {Seasonal Dinghy Instructor (Sailing)} % Job title
    {Tighnabruaich Sailing School} % Organization
    {UK, Tighnabruaich} % Location
    {Jul. 2015} % Date(s)
    {
    }

%---------------------------------------------------------
\end{cventries}
