
%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

    
%---------------------------------------------------------
  \cventry
    {Athlete} % Affiliation/role
    {Performance Sailing Experience} % Organization/group
    {International} % Location
    {2007 - Present} % Date(s)
    {
      I am a sailor who competes in many different types of sailing boats in races both nationally and internationally. In the time that I have been racing, I have become a World, European, British and Scottish champion. This has happened mainly in the J111 class of sailing yacht where I competed as part of a team of 8 on the boat, and in the Laser which is a one-person sailing dinghy. As part of my progression through the sport, I have been part of several performance programmes:
      \begin{itemize}
          \item UK U21 Youth squad.
          \item Scottish U19 Squad.
          \item The University of Edinburgh Individual Performance Programme.
          \item Supported by the Scottish Institute of Sport.
      \end{itemize}
      Being part of these programmes and working with the people in them is what has allowed me to achieve the success that I have. These experiences taught me how to achieve high-level targets through performance thinking and goal setting. These are skills which I apply in other areas of my life to help achieve targets. An important skill that I have developed while taking part in all of these sailing activities is time management. I have had to plan my training alongside other work such as school and university to be able to balance top-level sport with my education.
    }

%---------------------------------------------------------
  \cventry
    {Participant} % Affiliation/role
    {Google Hash Code} % Organization/group
    {Edinburgh} % Location
    % {Feb. 2018 \& Feb. 2019} % Date(s)
    {2018, 2019 \& 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Developed problem solving skills under pressure with a time limit.}
        \item {Working on team coding challenges in small groups.}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Participant} % Affiliation/role
    {Hacktoberfest, DigitalOcean} % Organization/group
    {Edinburgh} % Location
    {2018, 2019 \& 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Had my first real experience contributing to open-source projects.}
        \item {Learned the basics of GitHub to allow me to help contribute to other peoples work.}
      \end{cvitems}
    }
    
%---------------------------------------------------------

  \cventry
     {Participant}
     {Code Jam, Google}
     {Edinburgh}
     {2019 \& 2020}
     {
      Competitive programming working with a range of different algorithms to solve challenging problems against the clock.
     }

%---------------------------------------------------------
%   \cventry % Dosen't add much
%     {Athlete} % Affiliation/role
%     {MISC Sports} % Organization/group
%     {UK} % Location
%     {ADD DATES} % Date(s)
%     {
%      Along with my sailing experience I have also competed in other fun sporting activities. I was part of the universities novice rowing programme which involved training around 8 - 10 times a weeks to improve my skills and fitness. From this we went on to come 6th in the quad and 8th in the 8 at the British University novice championships (BUCS). I have also previously raced in skiing 
%     }

%---------------------------------------------------------

\end{cventries}